Computing with an Angry Poker Player

### 2014-09-25 draft0.tex
added labels for every section
added how paper is organized in the introduction

In this paper, we investigate the following problem set up:

@@

We also consider extensions of this problem set up where the earthquake hits all squares on the board at once. We refer to the former type of earthquake as $\textbf{local earthquakes}$ and earthquakes that hit the entire board as $\textbf{global earthquakes}$. 
\section{Definitions and Notation}

@@

\section{Acyclicity of Infinite Boards}

@@

\section{Board Variants: $n$-Trees}
\emph{written by Perry Kleinhenz, edited by Fermi Ma and Erik Waingarten.}\\

@@

\section{Order of Redistribution}

@@

\section{Computing with Chips}

>>>>

In this paper, we investigate the following problem:

@@

We also consider extensions of this problem set up where the earthquake hits all squares on the board at once. We refer to the former type of earthquake as $\textbf{local earthquakes}$ and earthquakes that hit the entire board as $\textbf{global earthquakes}$. \\

The paper is organized as follows. In Section~\ref{Definitions and Notation}, we formalize the terminology and operations we use to analyze the game. In Section~\ref{Stability of Finite Boards}, we introduce the idea of a potential function defined on boards to prove that all boards with a finite number of starting chips eventually stabilize. We then modify the potential function to work for infinite boards and we explore its consequences in Section~\ref{Acyclicity of Infinite Boards}. In Section~\ref{Order of Redistribution}, we show that the order in which local earthquakes happens does not matter, thus answering a question in the original problem statement. We then shift our approach in Section ADDSECTIONNAME and present results from our simulations of repeated earthquakes. In particular, we look at the starting arrangement where $n$ chips all start on the same square, and we conjecture based on experimental evidence that such arragnements stabilize after $\Theta(n \log n)$ global earthquakes. In Section~\ref{Board Variants: n-Trees}, we consider what happens when alternative board setups are considered. Finally, in Section~\ref{Computing with Chips} we present a model of computation based on the problem set up, and we show how to construct simple Boolean circuits with AND and OR gates. 
\section{Definitions and Notation}
\label{Definitions and Notation}

@@

\section{Acyclicity of Infinite Boards}
\label{Acyclicity of Infinite Boards}

@@

\section{Board Variants: $n$-Trees}
\label{Board Variants: n-Trees}
\emph{written by Perry Kleinhenz, edited by Fermi Ma and Erik Waingarten.}\\

@@

\section{Order of Redistribution}
\label{Order of Redistribution}

@@

\section{Computing with Chips}
\label{Computing with Chips}
